---
title: "Natalie's R Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Natalie's R Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753Natalie2025)
data("fire")
```
# Introduction
This is my package for class MATH-4753. This is a small collection of functions built throughout the course of the semester. scatterhist creates a scatterplot with histograms, myncurve plots a normal distribution and shades the specified area, myclt simulates the central limit theorem through repeated sampling, and mybin approximates a binomial distribution.

## First Function - scatterhist
Arguments:
x - x variable as vector
y - y variable as vector
xlab - x label
ylab - y label

This function creates a scatter plot of x vs y with histograms displayed on the edges. Histogram of x is on the top and for y its on the right. Here distance is our x and damage is our y.
```{r, echo=TRUE}
MATH4753Natalie2025::scatterhist(fire$DISTANCE, fire$DAMAGE, xlab = "distance", ylab = "damage")
``` 


## Second Function - myncurve
Arguments:
 mu - mean
 sigma - standard deviation
 a - the values of up to what point you want the graph shaded

This function draws the density curve of a normal distribution from mu - 3(sigma) to mu + 3(sigma) and shades the area under the curve up to a. Prints cummulative pobability and returns a list.
```{r, echo=TRUE}
MATH4753Natalie2025::myncurve(mu = 100, sigma = 15, a = 120)

```

Arguments:
n - sample size for each iteration
iter - number of iterations

This function takes n x iter values from the unifrom distribution on [0,5], the main purpose is to illustrate the central limit theorem. Returns histogram of sample sums
## Third Function - myclt
```{r, echo=TRUE}
#Invisible used here to avoid clutter from printing big list
invisible(MATH4753Natalie2025::myclt(n = 30, iter = 1000))

```

## Fourth Function - myBin
Arguments:

iter - number of iterations

n -number of trials

p - probability of success on single trial

This function approximates a binomial distribution by simualting repeated trials. In this example we simulate 100 binomial experiments with 10 trials each and success probability of 0.5
```{r, echo=TRUE}
MATH4753Natalie2025::mybin(iter = 100, n = 10, p = 0.5)

```
